Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-14 programlogic.tex
getting there on section 4

\begin{figure*}
  \begin{lstlisting}[language=Coq]
 Definition $\vaddr\mapsto_{\textsf{t}}\{\textsf{q}\}\; \vpage$ : vProp $\Sigma$ := 
  $\exists_{\textsf{l4e l3e l2e l1}} \ldotp$  $\ulcorner$ aligned $\vaddr \urcorner \ast$ L4_L1_PointsTo(maddr l4e l3e l2e l1e) $\ast$ addr_L1$(\vaddr,\textsf{l1e}) \mapsto_{p} \vpage$.
 Definition L4_L1_PointsTo (maddr l4e l3e l2e l1e :word 64) : vProp $\Sigma$ :=
 $\lambda$ cr3val.
  (l4M52 maddr cr3val) \$\sim$\ (l4off maddr cr3val) $\mapsto_{a}$ {q1}  l4e  $\ast$
  (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2}  l3e $\ast$ 
  (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e) $\mapsto_{a}$ {q3}  l2e $\ast$
  (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e) $\mapsto_{a}$ {q4}  l1e.
\end{lstlisting}
\caption{A Strong Virtual Points-to Relation}
\todo[inline,color=red]{Colin says: shouldn't ther be a fraction q in the body of the virtual pointsto def?
I know this is just a sketch that we then move away from, but it's worth getting accurate.}
\todo[inline,color=cyan]{Colin says: the virtual points-to here is not defined as a vprop! the body is an iProp,
containing an unbound variable rtv, which should be the cr3val taken as an argument. (Also, rtv doesn't make sense to me
as a shorthand, why not cr3val?). I'm also pretty sure the maddr in the virtual points-to definition should be va.}
  \label{fig:strongvirtualpointsto}
\end{figure*}

\subsection{An Overly-Restrictive Definition for Virtual Memory Addressing}
\label{sec:overly-restrictive}
One could give a naive logical definition to the virtual mememory addressing as conjuctions of each level translation 
(Figure \fref{fig:strongvirtualpointsto}). The very first assurance our logical constructions need to be able assert is 
the \textit{existence} of the page table walk. Our naive attempt shown in Figure \ref{figure:strongvirtualpointsto}, 
we see that a virtual address with a certain fractional permissions at each level of the page-table walk gives us sound 
assurance of the path existence reaching to a page table entry, consequently, with a full-ownership of page address, 
we can obtain and update the value mapped value at this physical page address through our virtual memory address.

The definition in Figure \ref{fig:strongvirtualpointsto} defines a virtual points-to assertion as
existentially quantifying the physical memory addresses of the individual entries in each page table,
asserting that a corresponding page table walk exists (\lstinline|L4_L1_PointsTo|), and then 
\todo[inline]{snapshot... the last bit of that assertion is weird, but I'll fix. I'll also just remove the fraction from that def since it gets
ignored anyways and we provide a better version shortly}
Given the definition of physical page-pointsto assertion and the root address of virtual-address space as shown in Figure \ref{fig:pagetable}, one can build the physical address-translation for a virtual address (e.g. \textsf{va}) via abstracting the L4-L1 table traversal as the following:
\begin{itemize}
  \item Level-4 Translation (L4): Performs the first level address translation to get the L4 entry (L4E) in Figure \ref{fig:pagetables} by using the masks l4M52 and l4off with \textsf{rtv} virtual base address to get the starting address of the L4 table (L4T), and locate the entry amongst 512 (q1) ones respectively.
    \begin{lstlisting}[language=Coq]
      $\hbox{(\TirNameStyle{{L4translate}})} \quad$ (l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1} l4e 
    \end{lstlisting}
 \item Level-3 Translation (L3): Performs the second level address translation to get the L3 entry (L3E) in Figure \ref{fig:pagetables} by using the masks l3M52 and l3off with L4 entry (l4e) to get the starting address of the L3 table (L3T), and locate the entry amongst 512 ones (q2) respectively.
    \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L3translate}})}$ (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2} l3e
    \end{lstlisting}
  \item Level-2 Translation (L2): Performs the second level address translation to get the L2 entry (L2E) in Figure \ref{fig:pagetables} by using the masks l2M52 and l2off with L3 entry (l3e) to get the starting address of the L2 table (L2T), and locate the entry amongst 512 ones (q3) respectively.
\begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L2translate}})}$ (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e)  $\mapsto_{a}$ {q3} l2e
    \end{lstlisting}
  \item Level-1 Translation (L1): Performs the second level address translation to get the L1 entry (L1E) in Figure \ref{fig:pagetables} by using the masks l1M52 and l1off with L2 entry (l2e) to get the starting address of the L1 table (L1T), and locate the entry amongst ones 512 (q4) respectively.
   \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L1translate}})}$ (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e)  $\mapsto_{a}$ {q4} l1e
    \end{lstlisting}
  \item Page Address Level Translation: Final computed physical page-address ($\textsf{addr\_L1}(\vaddr$,$\textsf{l1e}$)) points-to the value stored in the address ($\vpage$).
   \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{PageLevelAccess}})} \qquad$ addr_L1($\vaddr,\textsf{l1e}$) $\mapsto_{p} \vpage$.
    \end{lstlisting} 
\end{itemize}

\todo[inline]{Cite Kolanski here; not all of them, but some actually defined it exactly this way, for the current
address space.}
\subsection{Aliasing/Sharing Physical Pages}
  \label{sec:sharingpages}  
  One might have already observed that the virtual points-to definition shown in Figure \ref{fig:strongvirtualpointsto} 
  is too strong to specify some operations a virtual memory manager may need to do, such as
  move one level of the page table to a different physical location while preserving all virtual-to-physical mappings.\footnote{
    x86-64 hardware, like other architectures, includes a feature (which we do not formalize assertions for) to
    replace an L1 page table address in an L2 entry with a pointer to a \emph{larger} 2MB page (called super-pages), 
    or replace an L2 page table address in an L3 entry with a pointer to a 1GB page (called huge-pages).
  }
   To speak more concretely, the fractional permissions on the page-table-walk assertion ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ in Figure \ref{fig:strongvirtualpointsto}) 
  ensure fractional ownership of the four physical page table entries accessed by the hardware during address translation,
  as well as the physical memory holding the data of the virtual points-to.
  However, this formulation stores knowledge of the page table walk's details with ownership of the backing physical
  memory.
  Updating any of these mappings (e.g., move the page tables in physical memory, as in coallescing for
  superpages or hugepages)
  would require explicitly collecting all virtual points-to facts that traverse affected entries.
  It is preferable to permit the page tables themselves to be updated independently of the virtual points-to assertions,
  so long as those updates preserve the same virtual-to-physical translations.
\newcommand{\vale}{\textsf{val}}
\begin{figure*}
\todo[inline]{Colin says: again, this is supposed to be a vprop, but isn't doing anything with a cr3val argument.
I realize the GASI and per-address-space invariants, and therefore machinery to tie the virtual points-to
to the GASI, hasn't been introduced yet. Is there a short-hand here we can use to be ``more complete'' until the later text
that fills in these details?
}
\todo[inline,color=cyan]{Colin says: Oh!!! I see. You have that extremely subtle rtv subscript on the virtual points-to
syntax! Don't do that. First, it's really subtle and wasn't explained anywhere, so even I missed it. Second,
we're very explicitly describing vProps as functions from root to iProp. Sticking the rtv on the arrow there
is partly weird because it obscures which argument is really the vProp argument (there are 2 other word64s in that syntax),
partly weird because it's written next to something that \emph{isn't} a variable (the v subscript on the virtual points-to
arrow) while using the same font, and partly weird because when you actually write these assertions, rtv doesn't show
up in the syntax at all, which is the whole point --- virtual points-to defs shouldn't mention their cr3 or address space at
all!
Here's what I think it should look like (I also existentially quantified $\delta$ and fixed the p subscript on physical
points-to):
}
\[
\begin{array}{l}
    \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vale : \mathsf{vProp}~\Sigma \stackrel{\triangle}{=} 
    \exists \paddr\ldotp
    \exists \delta\ldotp
    \sumapaces{\mathit{cr3val}}\delta \ast 
  \sumwalkabs\vaddr\qfrac\paddr \ast \paddr \mapsto_{\mathsf{p}} \vale
\end{array}
\]
\todo[inline]{Colin says: The fact that we can't visually distinguish the variable v that is the value in memory
from the subscript v on the virtual points-to arrow is not ideal: it makes it hard to tell what's concrete syntax
and what's a variable. This is worth fixing, but near the bottom of the priority list}
\caption{Virtual-Pointsto for Sharing Pages}
  \label{fig:virtualpointstosharing}
\end{figure*}

@@

  \todo[inline]{Colin says: This requires explaining all the math here. Most reviewers of our paper will not be Iris
  experts. Even the notion of an authoritative RA is something you'd need to explain (the general idea of).
  So: write for non-Iris-expert readers. Above I explained the intuition behind the construction, so now we have to show
  that we correctly implemented that intuition in Iris. So explain authoritative RAs, and how the line below
  implements the intuition above.}
  To do so, we introduce the protocol separating read-only (fragmental) and authorative (full ownership) accesses to the page tables, specifically $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$. We realize this protocol by embedding it into an already existing \textsf{Iris}'s ghost-map (or view\_maps) construction
  \[\mathcal{A}\textsf{bsPTableWalk} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  (\mathcal{W}_{64} \; \rightarrow_{\textrm{fin}}\;  (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) ))\]
 where
  \begin{itemize}
  \item we decorate the fragmental ownership of the ghost-map ($ \sumwalkabs\vaddr\qfrac\paddr$) with the physical $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ whose ownership just ensures that the virtual address ($\vaddr$) is mapped to a page (referenced by $\paddr$)
  \item we place the authorative ownership $\mathcal{A}\textsf{PTableWalk}$ of the ghost-map in an address-space invariant ($\mathcal{I}$\textsf{ASpace} in Figure \ref{fig:peraspaceinvariant}) whose ownership grants sound update on the page table entries
  \end{itemize}

@@

\todo[inline]{Colin says: I can rewrite this remark into flowing text after you fully explain the math above.}
\begin{remark}[Exchanging Page-Table-Walk-Summarization Mappings (Tokens) under Mutation of Page Tables ]
  $\mathcal{A}\textsf{PTableWalk}$'s fragmental-ownership represents an individual key-value pair (per-virtual-address) which can be handled as a \textit{look-up} resource for an individual virtual address.
  To build more intuition on the convenience of this protocol, we can think of the use-case \textit{unmapping-pages}. Normally, in the existence of shared page-tables, we need to first collect all the fragmental map pairs, e.g. $\sumwalkabs\vaddr\qfrac\paddr$, then, after making sure of non-existence of \textit{sharing}, we can \textit{unmap} the page. In this case, it would be ok to put $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ and $ \sumwalkabs\vaddr\qfrac\paddr$ side-by-side inside the virtual-pointsto definition in Figure \ref{fig:virtualpointstosharing}. However, this pattern of verifying is not only inconvenient due to requirement of extra bookkeeping, but also violates our soundness argument based on considering  mutation on the shared page-tables -- due to coalescing of page tables etc. --. In other words, physical $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ sitting aside to  $ \sumwalkabs\vaddr\qfrac\paddr$ would be made invalid by any concurrent update on the physical page-table. So there should only be one physical memory resource inside the virtual pointsto definition: from physical page address to the value stored ($ \paddr \mapsto_{p} \vpage$).
\end{remark}

>>>>

\begin{figure*}
  \begin{lstlisting}[language=Coq]
 Definition $\vaddr\mapsto_{\textsf{t}}\{\textsf{q}\}\; \vpage$ : vProp $\Sigma$ := 
  $\exists_{\textsf{l4e l3e l2e l1}} \ldotp$  $\ulcorner$ aligned $\vaddr \urcorner \ast$ L4_L1_PointsTo(maddr l4e l3e l2e l1e) $\ast$ addr_L1$(\vaddr,\textsf{l1e}) \mapsto_{p}\{\mathsf{q}\} \vpage$.
 Definition L4_L1_PointsTo (maddr l4e l3e l2e l1e :word 64) : vProp $\Sigma$ :=
 $\lambda$ cr3val.
  (l4M52 maddr cr3val) \$\sim$\ (l4off maddr cr3val) $\mapsto_{a}$ {q1}  l4e  $\ast$
  (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2}  l3e $\ast$ 
  (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e) $\mapsto_{a}$ {q3}  l2e $\ast$
  (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e) $\mapsto_{a}$ {q4}  l1e.
\end{lstlisting}
\vspace{-1em}
\caption{A Strong Virtual Points-to Relation}
  \label{fig:strongvirtualpointsto}
\end{figure*}

\subsection{An Overly-Restrictive Definition for Virtual Memory Addressing}
\label{sec:overly-restrictive}
A natural definition for a virtual points-to that depends on the current address space is to
require that in order for a virtual address \textsf{va} to point to a value \textsf{v}, the assertion contains
partial ownership of the physical memory involved in the page table walk that would translate \textsf{va} to
its backing physical location --- with locations existentially quantified since a virtual points-to should not assert
\emph{which} locations are accessed in a page table walk.
Figure \ref{figure:strongvirtualpointsto} gives such a definition.
It asserts the existence of for page table entries, one at each translation level, and via \lstinline|L4_L1_PointsTo|
asserts from the current \lstinline|cr3| value, taking the offsets from \textsf{va} (as in Figure \ref{fig:pagetables})
to index each level, finding the existentially quantified entries in each level, 
ending with the L1 entry, whose physical page base is added to the page offset of \textsf{va} to obtain the physical address
 --- and there (\lstinline|addr_L1(va,l1e)|) in physical memory, is the value.
Most of the definition lives directly in \textsf{vProp}, using the separation logic structure lifted from Iris's \textsf{iProp}.

\lstinline|L4_L1_PointsTo| works by
chaining together the entries for each level, using the sequence of table offsets from the address being translated to index
each table level, and using the physical page address embedded in each entry.
For example, 
  the first level address translation to get the L4 entry (\lstinline|l4e|) 
  uses the masks \textsf{l4M52} with the current \lstinline|cr3| to get the 
  physical address of the start of the L4 table,
  and \textsf{l4off} with the virtual address being translated to compute the correct offset within that table.
  Then at that physical location is the appropriate entry in the L4 table \textsf{l4e}.
  Subsequent levels of the page table walk work similarly.
The statement of these assertions is simplified by the use of our split physical points-to assertions, since
each level of tables is page-sized.\footnote{We do not address superpages and hugepages in this paper.}
This helper definition is also a more explicit \textsf{vProp}, explicitly binding a value for \lstinline|cr3| and using it
to start the translation process.

% Given the definition of physical page-pointsto assertion and the root address of virtual-address space as shown in Figure \ref{fig:pagetable}, one can build the physical address-translation for a virtual address (e.g. \textsf{va}) via abstracting the L4-L1 table traversal as the following:
% \begin{itemize}
%   \item Level-4 Translation (L4): Performs 
%   the first level address translation to get the L4 entry (L4E) in Figure \ref{fig:pagetables} by using the masks l4M52 and l4off with \textsf{rtv} virtual base address to get the starting address of the L4 table (L4T), and locate the entry amongst 512 (q1) ones respectively.
%     \begin{lstlisting}[language=Coq]
%       $\hbox{(\TirNameStyle{{L4translate}})} \quad$ (l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1} l4e 
%     \end{lstlisting}
%  \item Level-3 Translation (L3): Performs the second level address translation to get the L3 entry (L3E) in Figure \ref{fig:pagetables} by using the masks l3M52 and l3off with L4 entry (l4e) to get the starting address of the L3 table (L3T), and locate the entry amongst 512 ones (q2) respectively.
%     \begin{lstlisting}[language=Coq]
%     $\hbox{(\TirNameStyle{{L3translate}})}$ (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2} l3e
%     \end{lstlisting}
%   \item Level-2 Translation (L2): Performs the second level address translation to get the L2 entry (L2E) in Figure \ref{fig:pagetables} by using the masks l2M52 and l2off with L3 entry (l3e) to get the starting address of the L2 table (L2T), and locate the entry amongst 512 ones (q3) respectively.
% \begin{lstlisting}[language=Coq]
%     $\hbox{(\TirNameStyle{{L2translate}})}$ (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e)  $\mapsto_{a}$ {q3} l2e
%     \end{lstlisting}
%   \item Level-1 Translation (L1): Performs the second level address translation to get the L1 entry (L1E) in Figure \ref{fig:pagetables} by using the masks l1M52 and l1off with L2 entry (l2e) to get the starting address of the L1 table (L1T), and locate the entry amongst ones 512 (q4) respectively.
%    \begin{lstlisting}[language=Coq]
%     $\hbox{(\TirNameStyle{{L1translate}})}$ (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e)  $\mapsto_{a}$ {q4} l1e
%     \end{lstlisting}
%   \item Page Address Level Translation: Final computed physical page-address ($\textsf{addr\_L1}(\vaddr$,$\textsf{l1e}$)) points-to the value stored in the address ($\vpage$).
%    \begin{lstlisting}[language=Coq]
%     $\hbox{(\TirNameStyle{{PageLevelAccess}})} \qquad$ addr_L1($\vaddr,\textsf{l1e}$) $\mapsto_{p} \vpage$.
%     \end{lstlisting} 
% \end{itemize}

This solution is in fact very close to that of \citet{kolanski08vstte}, who define a separation logic from scratch in \textsc{Isabelle/HOL},
where the semantics of all assertions are functions from pairs of heaps and page table root values to booleans.\footnote{
  This was a typical explicit construction at the time; their work significantly predates Iris.
}
Our solution removes some restrictions in this definition by further abstracting the handling of address translation.

\subsection{Aliasing/Sharing Physical Pages}
  \label{sec:sharingpages}  
  One might have already observed that the virtual points-to definition shown in Figure \ref{fig:strongvirtualpointsto} 
  is too strong to specify some operations a virtual memory manager may need to do, such as
  move one level of the page table to a different physical location while preserving all virtual-to-physical mappings.\footnote{
    x86-64 hardware, like other architectures, includes a feature (which we do not formalize assertions for) to
    replace an L1 page table address in an L2 entry with a pointer to a \emph{larger} 2MB page (called super-pages), 
    or replace an L2 page table address in an L3 entry with a pointer to a 1GB page (called huge-pages).
  }
   To speak more concretely, the fractional permissions on the page-table-walk assertion ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ in Figure \ref{fig:strongvirtualpointsto}) 
  ensure fractional ownership of the four physical page table entries accessed by the hardware during address translation,
  as well as the physical memory holding the data of the virtual points-to.
  However, this formulation stores knowledge of the page table walk's details with ownership of the backing physical
  memory.
  Updating any of these mappings (e.g., moving the page tables in physical memory, as in coallescing for
  superpages or hugepages)
  would require explicitly collecting all virtual points-to facts that traverse affected entries.
  It is preferable to permit the page tables themselves to be updated independently of the virtual points-to assertions,
  so long as those updates preserve the same virtual-to-physical translations.
\newcommand{\vale}{\textsf{val}}
\begin{figure*}
\[
\begin{array}{l}
    \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vale : \mathsf{vProp}~\Sigma \stackrel{\triangle}{=} \\
    \quad
    \exists \paddr\ldotp
    \exists \delta\ldotp
    \underbrace{\lambda\mathit{cr3val}\ldotp\sumapaces{\mathit{cr3val}}\delta}_\text{\begin{tabular}{c}Find ghost map for this\\address space\end{tabular}} \ast 
  \underbrace{\sumwalkabs\vaddr\qfrac\paddr }_\text{\begin{tabular}{c}Fractional ownership of \\virt-to-phys translation\end{tabular}}\ast 
  \underbrace{\paddr \mapsto_{\mathsf{p}} \vale}_\text{\begin{tabular}{c}Value at\\physical location\end{tabular}}
\end{array}
\]
\caption{Virtual-Pointsto for Sharing Pages}
  \label{fig:virtualpointstosharing}
\end{figure*}

@@

  % To do so, we introduce the protocol separating read-only (fragmental) and authorative (full ownership) accesses to the page tables, specifically $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$. 
  % We realize this protocol by embedding it into an already existing \textsf{Iris}'s ghost-map (or view\_maps) construction
  In Iris this is realized by using an authoritative resource algebra: there is a single \emph{authoritative} global copy of the (ghost)
  map caching virtual-to-physical address translations, and for each entry a read only \emph{partial} ownership of that key-value pair.
  The resource algebra itself is instantiated as:
  \[\mathcal{A}\textsf{bsPTableWalk} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  (\mathcal{W}_{64} \; \rightarrow_{\textrm{fin}}\;  (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) ))\]
We replace the physical
 $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$
with
fragmental ownership of the ghost-map ($ \sumwalkabs\vaddr\qfrac\paddr$),
 whose ownership just ensures that the virtual address ($\vaddr$) is mapped to a page (referenced by $\paddr$)

We place the authorative ownership $\mathcal{A}\textsf{PTableWalk}$ of the ghost-map in a per-address-space invariant
($\mathcal{I}$\textsf{ASpace} in Figure \ref{fig:peraspaceinvariant}) whose ownership, when combined with the
fraction stored in the virtual points-to, permits changes in the virtual-to-physical translations.
By itself, it allows changes to the page tables as long as they do not change the overall mappings from virtual
to physical addresses.
\todo[inline]{explain $\Theta$, $m$, and figure out where $\delta$ is bound in Figure \ref{fig:peraspaceinvariant}}

Another major change is that, because our logic is the first to explicitly address the existence of multiple address spaces,
the ghost map of virtual-to-physical translations (identified by the ghost name $\delta$ in Figure \ref{fig:virtualpointstosharing}
 \emph{for each address space}. This means we also require a way to locate the map for the current address space
from the current root page table pointer stored in \lstinline|cr3|.

\

@@

  % Colin removed this remark because it's skwtching a *3rd* alternative design for virtual points-to,
  % which could be useful for some readers, but will most likely just confuse
% \begin{remark}[Exchanging Page-Table-Walk-Summarization Mappings (Tokens) under Mutation of Page Tables ]
%   $\mathcal{A}\textsf{PTableWalk}$'s fragmental-ownership represents an individual key-value pair (per-virtual-address) which can be handled as a \textit{look-up} resource for an individual virtual address.
%   To build more intuition on the convenience of this protocol, we can think of the use-case \textit{unmapping-pages}. Normally, in the existence of shared page-tables, we need to first collect all the fragmental map pairs, e.g. $\sumwalkabs\vaddr\qfrac\paddr$, then, after making sure of non-existence of \textit{sharing}, we can \textit{unmap} the page. In this case, it would be ok to put $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ and $ \sumwalkabs\vaddr\qfrac\paddr$ side-by-side inside the virtual-pointsto definition in Figure \ref{fig:virtualpointstosharing}. However, this pattern of verifying is not only inconvenient due to requirement of extra bookkeeping, but also violates our soundness argument based on considering  mutation on the shared page-tables -- due to coalescing of page tables etc. --. In other words, physical $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ sitting aside to  $ \sumwalkabs\vaddr\qfrac\paddr$ would be made invalid by any concurrent update on the physical page-table. So there should only be one physical memory resource inside the virtual pointsto definition: from physical page address to the value stored ($ \paddr \mapsto_{p} \vpage$).
% \end{remark}
